---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R package: `wei.series.md.c1.c2.c3`

A likelihood model for series systems with Weibull component lifetimes.
Accounts for right-censoring and candidate sets indicative of masked failure
causes. 


## Related Publication

This library was developed to support the research presented in the following paper:

- "Reliability Estimation In Series Systems" - [GitHub](https://github.com/queelius/reliability-estimation-in-series-systems)

For detailed explanation and the scientific background behind the methodologies implemented in this library, please refer to the paper.

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of `wei.series.md.c1.c2.c3` from [GitHub](https://github.com/queelius/wei.series.md.c1.c2.c3) with:

``` r
# install.packages("devtools")
#devtools::install_github("queelius/wei.series.md.c1.c2.c3")
```

```{r}
library(algebraic.dist)
library(algebraic.mle)
library(wei.series.md.c1.c2.c3)
```

## Examples
```{r}
# fit the model
fit <- mle_numerical(mle_lbfgsb_wei_series_md_c1_c2_c3(
  df = guo_weibull_series_md$data,
  theta0 = c(1,1,1,1,1,1),
  control = list(
    maxit = 1000L,
    parscale = c(1, 1000, 1, 1000, 1, 1000))))

cbind(confint(fit),
  "fit" = params(fit),
  "guo mle" = guo_weibull_series_md$mle)

# log-likelihood
c("guo log-like" = guo_weibull_series_md$loglike, "fit log-like" = loglik_val(fit))
```

We see that they are approximately the same MLE fits.

```{r}
shapes <- params(fit)[seq(1, length(params(fit)), 2)]
scales <- params(fit)[seq(2, length(params(fit)), 2)]
data.frame(
  "Component Cause" = wei_series_cause(1L:3L, shapes = shapes, scales = scales),
  "Component MTTF" = wei_mttf(shape = shapes, scale = scales))

cat("System MTTF: ", wei_series_mttf(shapes = shapes, scales = scales))
```

```{r}
(tq <- qwei_series(p = .825, shapes = shapes, scales = scales))
surv_wei_series(t = tq, shapes = shapes, scales = scales)
rwei_series(10L, shapes =shapes, scales = scales)
pwei_series(seq(1, 5, 1), shapes = shapes, scales = scales)
```



## Brief Overview

This package implements a likelihood model for Weibull series systems from masked data,
including functions for the log-likelihood, score, and hessian of the log-likelihood.
Analytical solutions are provided for the log-likelihood and score functions, while
the hessian is computed numerically. The package is designed to handle two types of
data: masked component cause of failure data with exact failure time and right-censored
system lifetime data.

The masked component data should approximately satisfy certain conditions.
The conditions are as follows:

#### Condition 1

The component cause of failure is in the candidate set.

#### Condition 2

When we condition on the component cause of failure being any particular cause
in the canidate set and and the time of failure, the probability of the given
candidate set does not vary as we vary the component cause of failure.

#### Condition 3

The masking probabilities are independent of the series system lifetime
parameter vector.

### API
As a loglikelihood model, we provide the following functions:

- `loglik_wei_series_md_c1_c2_c3` for the log-likelihood
- `score_wei_series_md_c1_c2_c3` for the score function
- `hessian_wei_series_md_c1_c2_c3` for the hessian of the log-likelihood

For convenience, we also provide some wrappers around the `optim` function to solve
for the maximum likelihood estimates (MLE) of the shape and scale parameters using
the Nelder-Mead and simulated annealing algorithms:

- `mle_nelder_wei_series_md_c1_c2_c3` for the Nelder-Mead algorithm
- `mle_sann_wei_series_md_c1_c2_c3` for the simulated annealing algorithm

Since we base some of our results and analysis on Guo, Szidarovszky, and Niu (2013),
we provide the data set from their paper, along with the maximum likelihood estimates
of the shape and scale parameters for the Weibull series system. We also provide
a function to solve for the MLE using the Nelder-Mead algorithm:

- `guo_weibull_series_md` for a model that generates data similar to Guo, Szidarovszky, and Niu (2013)
- `guo_weibull_series_table_2` for the data from Table 2 in Guo, Szidarovszky, and Niu (2013)

We also provide a host of supporting functions and data tables, e.g.,
we provide Weibull series system distribution function that honors the
established conventions in R:

- `dwei_series` for the probability density function
- `pwei_series` for the cumulative distribution function
- `qwei_series` for the quantile function
- `rwei_series` for random number generation

We also provide functions to compute the mean time to failure and the
component cause of failure for the Weibull series distribution, along with
the hazard and survival functions:

- `wei_series_mttf` for the mean time to failure
- `wei_series_cause` for the component cause of failure
- `hazard_wei_series` for the hazard function
- `surv_wei_series` for the survival function (this is normally done by
  passing lower.tail = FALSE to `pwei_series` but we provide a function)

Finally, we also provide some functions for working with the components
of the Weibull series system, e.g., we provide a function to compute the
hazard function for the Weibull component lifetimes:

- `hazard_wei` for the hazard function of the Weibull component lifetimes
- `wei_mttf` for the mean time to failure of the Weibull component lifetimes
