---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R package: `wei.series.md.c1.c2.c3`

A likelihood model for series systems with Weibull component lifetimes.
Accounts for right-censoring and candidate sets indicative of masked failure
causes. 


## Related Publication

This library was developed to support the research presented in the following paper:

- "Reliability Estimation In Series Systems" - [GitHub](https://github.com/queelius/reliability-estimation-in-series-systems) | [Zenodo](https://doi.org/zenodo.XXXXX)

For detailed explanation and the scientific background behind the methodologies implemented in this library, please refer to the paper.

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of wei.series.md.c1.c2.c3 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("queelius/wei.series.md.c1.c2.c3")
```

```{r}
library(algebraic.dist)
library(algebraic.mle)
library(wei.series.md.c1.c2.c3)
```


```{r}
# fit the model
fit <- mle_numerical(mle_lbfgsb_wei_series_md_c1_c2_c3(
  df = guo_weibull_series_md$data,
  theta0 = c(1,1,1,1,1,1),
  control = list(
    maxit = 1000L,
    parscale = c(1, 1000, 1, 1000, 1, 1000))))

cbind(confint(fit),
  "fit" = params(fit),
  "guo mle" = guo_weibull_series_md$mle)

# log-likelihood
c("guo log-like" = guo_weibull_series_md$loglike, "fit log-like" = loglik_val(fit))
```

We see that they are approximately the same MLE fits.


```{r}
shapes <- params(fit)[seq(1, length(params(fit)), 2)]
scales <- params(fit)[seq(2, length(params(fit)), 2)]

# make a 5x3 matrix, col1 = component j, col2 = component cause of probability for component j, and col 3 = mttf of component j
cause <- wei_series_cause(1L:5L, shapes = shapes, scales = scales)
comp_mttf <- numeric(length=5)
for (i in 1:5) comp_mttf[i] <- wei_mttf(shape = shapes[i], scale = scales[i])


wei_series_mttf(shapes = shapes, scales = scales)
```


```{r}
tq <- qwei_series(q = .825, shapes = shapes, scales = scales)
surv_wei_series(p = tq, shapes = shapes, scales = scales)
hazard_wei_series 
pwei_series(seq(1, 5, 1), param(fit))
wei_series_cause(1L:5L, shapes = shapes, scales = scales)
wei_series_mttf(shapes = shapes, scales = scales)

dwei_series 
rwei_series(10L, shapes = fit.shapesparam(fit)
```